Multi-Task Mutual Learning for Vehicle Re-Identification

### 2019-05-16 paper.tex
A number of minor corrections to the paper.

%%%%%%%%% ABSTRACT
\begin{abstract}
Vehicle re-identification (Re-ID) aims to search a specific vehicle
instance across non-overlapping camera views.
%
The main challenge of vehicle Re-ID is that
the visual appearance of vehicles may drastically changes
according to diverse viewpoints and illumination.
%
Most of existing vehicle Re-ID model cannot make full use of
various complementary vehicle information, e.g. vehicle type and orientation.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative features simultaeously from multiple branches.
%
Specially, we design a consensus learning loss function by fusing features from the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of our
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the a large-scale benchmarks VeRi-776.
We also yield competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
\end{abstract}

@@

%% Background of vehicle Re-ID
With the development of autonomous driving
and smart city applications, the need to accurately analyze vehicles on urban streets
via multiple computer vision tasks such as detection, classification and
pose estimation, as well as re-identification, is ever-increasing.
%
Specially, vehicle re-identification has attracted increasing attention in the research community
\cite{liu2016vehicleid,liu2016veri,liu2016veri,
wang2017orientation,Wang_2017_ICCV,Zhou2018VAMI},
as it can play an important role in
intelligent transportation systems and public safety.

@@

% Existing work's problem
Most previously proposed vehicle Re-ID methods \cite{liu2016vehicleid,liu2016veri,Shen_2017_ICCV,Zhou2018VAMI} focus on using a single branch
to learn an embedded feature representation for vehicle instance re-identification
from the original information (e.g. the original whole vehicle image).
%
Due to the previously mentioned challenges for vehicle re-identification,
this single branch structure can not take advantage of the diversity of vehicles.
%
Moreover, most existing works
\cite{liu2016vehicleid,liu2016veri}
train their vehicle Re-ID deep learning model
using a single supervisory signal (e.g. vehicle ID).
%
However, we argue that vehicle ID label {\em alone} can not differentiate the differences between vehicles due to the issues we raised above. But additionally we can make use of the fact that the orientation of a vehicle alters its view in a predictable manner.
As a result, we suggest that imposing multiple and different supervisory signals
simultaneously - the vehicle ID \emph{and} vehicle orientation - allows the model to learn this variation in a more well-defined manner, and is thus more effective
for learning the fine-grained discriminative features necessary for vehicle
Re-ID. As orientation labels were provided by Wang \etal \cite{Wang_2017_ICCV} for the VeRi dataset \cite{liu2016veri}, is is possible to make use of these multiple signals for this purpose. Examples of the orientation labels provided by this paper can be seen in Figure \ref{F:veri_veh_orientations}.

@@

\noindent {\bf Vehicle Re-Identification. }
%Whist vehicle Re-ID is less studied than person Re-ID
%\cite{gong2014person,li2018harmonious,zhong2017camera},
%there are a handful of existing methods.
%Notably, Feris \etal \cite{feris2012large} proposed an attribute-based Re-ID method.
%The vehicles are firstly classified by different attributes like car model types and colours. The Re-ID matching is then conducted in the attribute space.
%%
%Dominik \etal \cite{zapletal2016vehicle}
%used 3D bounding boxes for rectifying car images and then concatenate colour histogram features of vehicle image pairs.
%A binary linear SVM model is then trained to verify whether a pair of images have the same identity.
%%
%Both methods rely heavily on weak hand-crafted visual features in a
%complex multi-step based approach, suffering from weak discriminative model generalisation.
A number of deep learning techniques have been exploited for the purpose vehicle Re-ID. For instance, Liu
\etal \cite{liu2016veri} explored a deep neural network to estimate the
visual similarities between vehicle images.
%Vehicle appearances, spatio-temporal information and license plates are
%independently and incrementally used to improve the similarity function for
%vehicle matching.  they use a deep neural network to estimate the visual
%similarities between vehicle images for enjoying the strong representation
%learning capacity.
%
Liu \etal \cite{liu2016vehicleid} also designed a Coupled Clusters Loss (CCL)
to boost a multi-branch CNN model for vehicle Re-ID.
%
All these methods utilize the global appearance features of vehicle images and
ignore local discriminative regions.
%
To explore local information motivated by the idea of landmark alignment
\cite{zhang2014facial} in both face recognition \cite{taigman2014deepface} and
human body pose estimation \cite{newell2016stacked}, Wang \etal
\cite{Wang_2017_ICCV} considered 20 vehicle keypoints for learning and aligning
local regions of a vehicle for Re-ID.  Clearly, this approach comes with extra
cost of exhaustively labelling these keypoints in a large number of vehicle
images, and the implicit assumption of having sufficient image
resolution/details for extracting these keypoints.
%

@@

\subsection{Datasets}
We employ two Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively. Firstly we conduct experiments on a benchmark dataset, VeRi-776 \cite{liu2016veri}, which has been widely tested by the majority of recent works. And secondly we employ the new CityFlow dataset \cite{tang2019cityflow}, a challenging dataset that has been shown to be more difficult than previous publicly available benchmarks.
%
The VeRi-776 dataset \cite{liu2016veri} has 37,778 images of 576 IDs in the training set and 200
IDs in the test set. The standard probe and gallery sets consist of 1,678 and 11,579
images, respectively. There are also orientation labels, for 8 possible orientations, available for the VeRi-776 dataset, which were provided by \cite{Wang_2017_ICCV}.
%
%% The VehicleID \cite{liu2016vehicleid} dataset provides a training set with 113,346 from 13,164 IDs and a test set
%% with 19,777 images from 2,400 identities. It adopts the single-shot re-id setting,
%% with only one true matching for each probe. Following the standard setting, we
%% repeated 10 times of randomly selected probe and gallery sets in our experiments.
%
The CityFlow dataset \cite{tang2019cityflow} has 36,935 images of 333 IDs in the training set and 333 different IDs in the test set. The standard probe and gallery sets consist of 1,052 and 18,290 images respectively.
The data split statistics of both datasets are summarised in Table \ref{T:dataset_details}.

@@

\subsection{Evaluation on Veri776 Dataset}
Firstly, we train and test on the VeRi-776 dataset in order to compare with
existing state-of-the-art methods with identical settings. In order to experiment the benefit of adding each of the separate branches of our model, we take branch A (vehicle identity) as our central branch, and of course all models have an E consensus branch, and then perform experiments where we include each of the other branches in turn. So MTML-S refers to a model built from branches A, B and E only, MTML-G has branches A, C and E only, and so on. We then test versions of the model with three branches (e.g. MTML-SG includes branches A, B, C and E).  
MTML-OSG (branches A, B, C, D and E) is then our full model, and MTML-OSG (ReRank \cite{zhong2017re}) the results of the full model after additional re-ranking. Table \ref{T:benchmark_results_veri} shows the results of this
experiment, with all experiments run for 150 epochs of training. As can be seen,
even before re-ranking, our full model achieves state-of-the-art mAP
and Rank-1 scores on this dataset, of 64.6\% and 92.3\%
respectively. And after re-ranking the mAP score is increased to an
impressive 68.3\%.

@@

    \caption{
        Qulitative comparison of example query images between expriment with
        and without orientaion branch.
        Rank-1 to Rank-10 is shown. Each pair compares MTML-SG
        (upper) to MTML-OSG (below) trained and tested on the VeRi-776. 
        AP refers to Average Precision of that query. 
    }
    \label{fig:ranks}
%    \vspace{-0.7cm}
\end{figure*}

@@

Two groups of experiments are conducted on CityFlow benchmark: 
(1) Training on CityFlow, and (2) Training on CityFlow and VeRi-776.
%
For the first group experiment, we trained MTML-S (branch A, B and E), 
MTML-G (branch A, C and E) and MTML-SG model only on CityFlow training data.
Table \ref{T:cityflow_results} shows that: 
(1) -G branch combination is much better than -S branch combination. 
The potential reason is that grayscale analysis is more useful than mult-scale in vehicle Re-ID.
(2) Joint learning with -S and -G is better than any individual one of them on mAP evaluation.
Another interesting thing is that
after re-ranking algorithm, mAP performance improves while CMC performace drops.
The possible reason is that more similar image vehicles will get close after re-ranking.
This means some false matching images at high rank will ``attract'' more false matching images after re-ranking.
In such a case, it will impact CMC performance.

%The reason of combine VeRi-776 dataset into training set is that
Since the orientation label is only available in VeRi-776, 
for training the full MTML model including orientation supervisory signal,
we did the second group experiment.
%
Table \ref{T:cf_veri_res} shows that: 
(1) By adding VeRi-776 training data,
with MTML-S, MTML-G and MTML-SG, 
we all obtain the better mAP and CMC performance on CityFlow
than the model only training on CityFlow.
Meanwhile, the mAP and CMC performance is a slightly lower on VeRi-776
than the model only training on VeRi-776. We suspect this is due to training
for 100 epochs, compared to 150.
(2) By adding orientation branch, MLTML-OSG totaling 4 bracnhes, 
we obtian the best mAP performance {62.6\%} and {23.6\%} on VeRi-776 and
CityFlow repectively. 
This shows that our mutual learning between orientation branch supervised by orientation label and other branches supervised by ID label is effective.

@@

Qualitative result comparison with or without orientation branch are shown in
Figure~\ref{fig:ranks}. The advantage of learning orientation and ID signal can
be seen in each pair where in MTML-OSG different views of the same ID vehicle
are ranked higher compared to MTML-SG (Figure~\ref{fig:ranks}(a,b,d)). It can also be observerd that similar
viewpoints better grouped together in the ranks (Figure~\ref{fig:ranks}(c,d)).

@@

\section{Conclusions}
Vehicle Re-ID is difficult because the visual appearance of
a vehicle instance may drastically change due to diverse
viewpoints and illumination, whilst different vehicle instances of the same
model type may have a very similar appearance.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative feature simultaeously from multiple branches.
%
Moreover, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the a existing large-scale benchmarks VeRi-776.
%VehicleID and
We also yield a competitive performance on the NVIDIA 2019 AI City Challenge Track 2.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Vehicle re-identification (Re-ID) aims to search a specific vehicle
instance across non-overlapping camera views.
%
The main challenge of vehicle Re-ID is that
the visual appearance of vehicles may drastically changes
according to diverse viewpoints and illumination.
%
Most existing vehicle Re-ID models cannot make full use of
various complementary vehicle information, e.g. vehicle type and orientation.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative features simultaneously from multiple branches.
%
Specifically, we design a consensus learning loss function by fusing features from the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of our
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on a large-scale benchmark dataset, VeRi-776.
We also yield competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
\end{abstract}

@@

%% Background of vehicle Re-ID
With the development of autonomous driving
and smart city applications, the need to accurately analyze vehicles on urban streets
via multiple computer vision tasks such as detection, classification and
pose estimation, as well as re-identification, is ever-increasing.
%
Specially, vehicle re-identification has attracted increasing attention in the research community
\cite{liu2016vehicleid,liu2016veri,liu2016veri,
wang2017orientation,wang2017orientation,Zhou2018VAMI},
as it can play an important role in
intelligent transportation systems and public safety.

@@

% Existing work's problem
Most previously proposed vehicle Re-ID methods \cite{liu2016vehicleid,liu2016veri,Shen_2017_ICCV,Zhou2018VAMI} focus on using a single branch
to learn an embedded feature representation for vehicle instance re-identification
from the original information (e.g. the original whole vehicle image).
%
Due to the previously mentioned challenges for vehicle re-identification,
this single branch structure can not take advantage of the diversity of vehicles.
%
Moreover, most existing works
\cite{liu2016vehicleid,liu2016veri}
train their vehicle Re-ID deep learning model
using a single supervisory signal (e.g. vehicle ID).
%
However, we argue that vehicle ID label {\em alone} can not differentiate the differences between vehicles due to the issues we raised above. But additionally we can make use of the fact that the orientation of a vehicle alters its view in a predictable manner.
As a result, we suggest that imposing multiple and different supervisory signals
simultaneously (e.g. the vehicle ID \emph{and} vehicle orientation) allows the model to learn this variation in a more well-defined manner, and is thus more effective
for learning the fine-grained discriminative features necessary for vehicle
Re-ID. As orientation labels were provided by Wang \etal \cite{wang2017orientation} for the VeRi dataset \cite{liu2016veri}, is is possible to make use of these multiple signals for this purpose. Examples of the orientation labels provided by this paper can be seen in Figure \ref{F:veri_veh_orientations}.

@@

\noindent {\bf Vehicle Re-Identification. }
%Whist vehicle Re-ID is less studied than person Re-ID
%\cite{gong2014person,li2018harmonious,zhong2017camera},
%there are a handful of existing methods.
%Notably, Feris \etal \cite{feris2012large} proposed an attribute-based Re-ID method.
%The vehicles are firstly classified by different attributes like car model types and colours. The Re-ID matching is then conducted in the attribute space.
%%
%Dominik \etal \cite{zapletal2016vehicle}
%used 3D bounding boxes for rectifying car images and then concatenate colour histogram features of vehicle image pairs.
%A binary linear SVM model is then trained to verify whether a pair of images have the same identity.
%%
%Both methods rely heavily on weak hand-crafted visual features in a
%complex multi-step based approach, suffering from weak discriminative model generalisation.
A number of deep learning techniques have been exploited for the purpose vehicle Re-ID. For instance, Liu
\etal \cite{liu2016veri} explored a deep neural network to estimate the
visual similarities between vehicle images.
%Vehicle appearances, spatio-temporal information and license plates are
%independently and incrementally used to improve the similarity function for
%vehicle matching.  they use a deep neural network to estimate the visual
%similarities between vehicle images for enjoying the strong representation
%learning capacity.
%
Liu \etal \cite{liu2016vehicleid} also designed a Coupled Clusters Loss (CCL)
to boost a multi-branch CNN model for vehicle Re-ID.
%
All these methods utilize the global appearance features of vehicle images and
ignore local discriminative regions.
%
To explore local information motivated by the idea of landmark alignment
\cite{zhang2014facial} in both face recognition \cite{taigman2014deepface} and
human body pose estimation \cite{newell2016stacked}, Wang \etal
\cite{wang2017orientation} considered 20 vehicle keypoints for learning and aligning
local regions of a vehicle for Re-ID.  Clearly, this approach comes with extra
cost of exhaustively labelling these keypoints in a large number of vehicle
images, and the implicit assumption of having sufficient image
resolution/details for extracting these keypoints.
%

@@

\subsection{Datasets}
We employ two Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively. Firstly we conduct experiments on a benchmark dataset, VeRi-776 \cite{liu2016veri}, which has been widely tested by the majority of recent works. And secondly we employ the new CityFlow dataset \cite{tang2019cityflow}, a challenging dataset that has been shown to be more difficult than previous publicly available benchmarks.
%
The VeRi-776 dataset \cite{liu2016veri} has 37,778 images of 576 IDs in the training set and 200
IDs in the test set. The standard probe and gallery sets consist of 1,678 and 11,579
images, respectively. There are also orientation labels, for 8 possible orientations, available for the VeRi-776 dataset, which were provided by \cite{wang2017orientation}.
%
%% The VehicleID \cite{liu2016vehicleid} dataset provides a training set with 113,346 from 13,164 IDs and a test set
%% with 19,777 images from 2,400 identities. It adopts the single-shot re-id setting,
%% with only one true matching for each probe. Following the standard setting, we
%% repeated 10 times of randomly selected probe and gallery sets in our experiments.
%
The CityFlow dataset \cite{tang2019cityflow} has 36,935 images of 333 IDs in the training set and 333 different IDs in the test set. The standard probe and gallery sets consist of 1,052 and 18,290 images respectively.
The data split statistics of both datasets are summarised in Table \ref{T:dataset_details}.

@@

\subsection{Evaluation on Veri776 Dataset}
Firstly, we train and test on the VeRi-776 dataset in order to compare with
existing state-of-the-art methods with identical settings. In order to experiment the benefit of adding each of the separate branches of our model, we take branch A (vehicle identity) as our central branch, and all models have an E consensus branch. We then perform experiments where we include each of the other branches in turn. So MTML-S refers to a model built from branches A, B and E only, MTML-G has branches A, C and E only, and so on. We then test versions of the model with three branches plus E (e.g. MTML-SG includes branches A, B, C and E).
MTML-OSG (branches A, B, C, D and E) is then our full model, and MTML-OSG (ReRank \cite{zhong2017re}) the results of the full model after additional re-ranking. Table \ref{T:benchmark_results_veri} shows the results of this, with all experiments run for 150 epochs of training. As can be seen,
even before re-ranking, our full model achieves state-of-the-art mAP
and Rank-1 scores on this dataset, of 64.6\% and 92.3\%
respectively. And after re-ranking the mAP score is increased to an
impressive 68.3\%.

@@

    \caption{
        Qualitative comparison of example query images between experiments with
        and without inclusion of the orientaion branch.
        Rank-1 to Rank-10 is shown. Each pair compares MTML-SG
        (upper) to MTML-OSG (below) trained and tested on the VeRi-776.
        AP refers to Average Precision of that query.
    }
    \label{fig:ranks}
%    \vspace{-0.7cm}
\end{figure*}

@@

Two sets of experiments are conducted on CityFlow benchmark:
(1) Training on CityFlow, and (2) Training on CityFlow and VeRi-776.
%
For the first set of experiments, we trained MTML-S (branch A, B and E),
MTML-G (branch A, C and E) and MTML-SG model only on CityFlow training data.
Table \ref{T:cityflow_results} shows that:
(1) MTML-G branch combination is much better than MTML-S branch combination.
The potential reason is that grayscale analysis is more useful than mult-scale in vehicle Re-ID.
(2) Joint learning with MTML-SG is better than any individual one of them on mAP evaluation.
Another interesting observation is that
after re-ranking algorithm, mAP performance improves while CMC performace drops.
The possible reason is that more similar image vehicles will get close after re-ranking.
This means some false matching images at high rank will ``attract'' more false matching images after re-ranking.
In such a case, it will impact CMC performance.

%The reason of combine VeRi-776 dataset into training set is that
Since the orientation label is only available in VeRi-776,
for training the full MTML model including orientation supervisory signal,
we did the second experiment which included both this database plus CityFlow.
%
Table \ref{T:cf_veri_res} shows that:
(1) By adding VeRi-776 training data,
with MTML-S, MTML-G and MTML-SG,
we all obtain a better mAP and CMC performance on CityFlow
than the model which was only trained on CityFlow.
Meanwhile, the mAP and CMC performance is a slightly lower on VeRi-776
than the model only training on VeRi-776. We suspect this is due to training
for a shorter period of time, as this experiment ran for only 100 epochs, compared to 150.
(2) By adding orientation branch, the MLTML-OSG model totalling 4 branches,
we obtain the best mAP performance {62.6\%} and {23.6\%} on VeRi-776 and
CityFlow respectively.
This shows that our method of mutual learning between the orientation branch supervised by orientation labels and the other branches supervised by ID label is effective.

@@

Qualitative results showing a comparison of rankings with or without orientation branch are shown in Figure~\ref{fig:ranks}. The advantage of learning both the orientation and ID signal can
be seen in each pair where the MTML-OSG model is able to rank very different views of the same ID vehicle highly, which compares to the MTML-SG model which can only find images containing similar viewpoints, many of which are incorrect IDs (Figure~\ref{fig:ranks}(a,b,d)). It can also be observerd that similar viewpoints are better grouped together in the ranks (Figure~\ref{fig:ranks}(c,d)).

@@

\section{Conclusions}
Vehicle Re-ID is a difficult problem due to the fact that the visual appearance of
a vehicle instance may drastically change due to diverse
viewpoints and illumination, whilst different vehicle instances of the same
model type may have a very similar appearance.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative feature simultaeously from multiple branches.
%
Moreover, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the a existing large-scale benchmarks VeRi-776.
%VehicleID and
We also yield a competitive performance on the NVIDIA 2019 AI City Challenge Track 2.

\section{Acknowledgements}
